Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles

### 2022-10-12 paperIEEE-ROSE2022-Pres.tex
IEEE ROSE Presentation and Paper Work
I made some slight changes to the presentation and added to the paper abstract

\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman \and Md Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\begin{frame}

  Therefore, approximated output signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \mathbf{y} = \mathbf{W}^T\bm{\sigma}(\mathbf{x}),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{p}$ with components of weight matrix ${\bf W}$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W} = 
  \begin{bmatrix}
    w^{1,1} &  w^{1,2} & \ldots &w^{1,m}\\
    w^{2,1} & w^{2,2}& \ldots &w^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w^{p,1} & w^{p,2}& \ldots &w^{p,m}
  \end{bmatrix}.
\end{align*}
%

Now take $\eta$ data points and form the set of linear equations as: %
%
\begin{align*}
&  \bm{\sigma}^T(\mathbf{x}_k) \mathbf{W}  \approx     \left(\mathbf{y}_{k}^{[d]}\right)^T\\
 & \bm{\sigma}^T(\mathbf{x}_{k+1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+1}^{[d]}\right)^T\\
                                            &\vdots \\
 & \bm{\sigma}^T(\mathbf{x}_{k+\eta-1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+\eta-1}^{[d]}\right)^T  
\end{align*}
%
\end{frame}

\begin{frame}
  In compact form:
  \begin{align*}
    \bm{\Sigma}\mathbf{W} \approx  \mathbf{U}^{[d]},\qquad\text{with}
    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  \end{align*}
  %
  $\mathbb{R}^{\eta\times p}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf x}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf y}_{\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$

  Let $\bm{\Sigma}\mathbf{W}\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta$ can be written as:
  \begin{align*}
    \delta = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
  \end{align*}

Weight matrix ${\bf W}$ can then be found minimizing the sum--of--square error $\delta$ defined by %
%
\begin{align*}
  \delta = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W})^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W})\right].
\end{align*}
%
Taking the derivative of $\delta$ with respect to ${\bf W}$ yields 
%
\begin{align}
  \frac{\partial\delta}{\partial\mathbf{W}} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}
  \label{eq:actorWeightsGradient}
\end{align}
%

\begin{frame}

  Setting $\frac{\partial\delta}{\partial\mathbf{W}}$ to zero yeilds
  \begin{align*}
    {\bf W} = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
  \end{align*}

$\bullet$ Hidden layer to output layer weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:

\begin{multline}
  \mathbf{W}^{(r+1)} = \mathbf{w}^{(r)} - \ell\frac{\partial\delta}{\partial\mathbf{W}}= \mathbf{W}^{(r)} - \ell\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}^{(r)}\right)\\
  = \mathbf{w}^{(r)}-\ell \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}^{(r)} - \mathbf{U}^{[d]}\right)
  \label{eq:actorWeightUpdate}
\end{multline}

>>>>

\author[H.~Grady, N.~Nauman, Md Suruz~Miah]{Hannah~Grady \and Nicholas~Nauman \and Md Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

%\begin{frame}
%
%  Therefore, approximated output signal can be written as:
%\begin{align}
%  \label{eq:approximatePolicyActorWeights}
%    \mathbf{y} = \mathbf{W}^T\bm{\sigma}(\mathbf{x}),
%  \end{align}
%%
%where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{p}$ with components of weight matrix ${\bf W}$ shown in Fig.~\ref{fig:nnActor} are given by %
%%
%\begin{align*}
%  {\bf W} = 
%  \begin{bmatrix}
%    w^{1,1} &  w^{1,2} & \ldots &w^{1,m}\\
%    w^{2,1} & w^{2,2}& \ldots &w^{1,m}\\
%    \vdots & \ddots & \ldots &\vdots\\
%    w^{p,1} & w^{p,2}& \ldots &w^{p,m}
%  \end{bmatrix}.
%\end{align*}
%%
%
%Now take $\eta$ data points and form the set of linear equations as: %
%%
%\begin{align*}
%&  \bm{\sigma}^T(\mathbf{x}_k) \mathbf{W}  \approx     \left(\mathbf{y}_{k}^{[d]}\right)^T\\
% & \bm{\sigma}^T(\mathbf{x}_{k+1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+1}^{[d]}\right)^T\\
%                                            &\vdots \\
% & \bm{\sigma}^T(\mathbf{x}_{k+\eta-1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+\eta-1}^{[d]}\right)^T  
%\end{align*}
%%
%\end{frame}

%\begin{frame}
%  In compact form:
%  \begin{align*}
%    \bm{\Sigma}\mathbf{W} \approx  \mathbf{U}^{[d]},\qquad\text{with}
%    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
%  \end{align*}
%  %
%  $\mathbb{R}^{\eta\times p}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf x}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf y}_{\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$
%
%  Let $\bm{\Sigma}\mathbf{W}\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta$ can be written as:
%  \begin{align*}
%    \delta = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
%  \end{align*}
%
%Weight matrix ${\bf W}$ can then be found minimizing the sum--of--square error $\delta$ defined by %
%%
%\begin{align*}
%  \delta = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W})^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W})\right].
%\end{align*}
%%
%Taking the derivative of $\delta$ with respect to ${\bf W}$ yields 
%%
%\begin{align}
%  \frac{\partial\delta}{\partial\mathbf{W}} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}
%  \label{eq:actorWeightsGradient}
%\end{align}
%%
%
%\end{frame}

%\begin{frame}
%
%
%  Setting $\frac{\partial\delta}{\partial\mathbf{W}}$ to zero yields
%  \begin{align*}
%    {\bf W} = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
%  \end{align*}
%  
%$\bullet$ Hidden layer to output layer weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:
%
%\begin{multline}
%  \mathbf{W}^{(r+1)} = \mathbf{w}^{(r)} - \ell\frac{\partial\delta}{\partial\mathbf{W}}= \mathbf{W}^{(r)} - \ell\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}^{(r)}\right)\\
%  = \mathbf{w}^{(r)}-\ell \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}^{(r)} - \mathbf{U}^{[d]}\right)
%  \label{eq:actorWeightUpdate}
%\end{multline}
%
%\end{frame}
